Job Demands-Resources model components through the lens of O*NET classifications

### 2022-12-02 Submission.Rmd
Fixed the YAML
formatting mostly

We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.O\*NETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 "work activity" classifications which O\*NET groups into categories of "Information Input" (5 statements), "Interacting with Others" (17 statements), "Mental Processes" (10 statements) and "Work Output" (9 statements). 57 "work context" statements grouped into "Interpersonal Relationships" (14 statements), "Physical Work Conditions" (30 statements), and "Structural Job Characteristics" (13 statements).

These "descriptors" often have unique response categories ([see here for example](https://www.O\*NETonline.org/find/descriptor/result/4.C.1.c.2)). We retained the O\*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

The below graphs present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.

> Note. The "zero" standard deviations are likely one person, *n*'s should also go on these graphs if they're retained.

```{r resourceslowsd}

@@

```{r challengesagree}

@@

```{r hindrancesagree}

@@

@@

The below graphs present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

```{r resourceshisd}

@@

```{r challengeshighsd}

@@

```{r hindranceshighsd}

@@

@@

#check the autonomy variables
summary(data$hindrance_autonomy)
summary(data$challenge_autonomy)
summary(data$resource_autonomy)
library(tidyr)

@@

table(toplot$onet)

@@

>>>>

We used 98 statements taken from O\*NET ["activity" and "context" classifications](https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3). We retained 41 "work activity" classifications which O\*NET groups into categories of "Information Input" (5 statements), "Interacting with Others" (17 statements), "Mental Processes" (10 statements) and "Work Output" (9 statements). 57 "work context" statements grouped into "Interpersonal Relationships" (14 statements), "Physical Work Conditions" (30 statements), and "Structural Job Characteristics" (13 statements).

These "descriptors" often have unique response categories ([see here for example](https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2)). We retained the O\*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had *at least some relevance* to their job was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

```{r resourcesagree, fig.cap="Characteristics most similarly viewed as resources (lowest standard deviations)."}

@@

```{r challengesagree, fig.cap="Characteristics most similarly viewed as challenges (lowest standard deviations)."}

@@

```{r hindrancesagree, fig.cap="Characteristics most similarly viewed as hindrances (lowest standard deviations)."}

@@

Figures \@ref(fig:resourcesagree), \@ref(fig:challengesagree), and \@ref(fig:hindrancesagree) present the resources, challenges, and hindrances that are *largely agreed on* as indexed by (relatively) low standard deviations.[^caveat]

[^caveat]: There were a few characteristics with standard deviations of "zero" but these were excluded from presenation as they were likely representing only one person (*n*'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).

@@

```{r resourcesdisagree, fig.cap="Characteristics most *dis*similarly viewed as resources (highest standard deviations)."}

@@

```{r challengesdisagree, fig.cap="Characteristics most *dis*similarly viewed as challenges (highest standard deviations)."}

@@

```{r hindrancesdisagree, fig.cap="Characteristics most *dis*similarly viewed as hindrances (highest standard deviations)."}

@@

Figures \@ref(fig:resourcesdisagree), \@ref(fig:challengesdisagree), and \@ref(fig:hindrancesdisagree) present the resources, challenges, and hindrances that are *largely disagreed on* as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

@@

#check the autonomy variables
#summary(data$hindrance_autonomy)
#summary(data$challenge_autonomy)
#summary(data$resource_autonomy)

library(tidyr)

@@

#table(toplot$onet)

@@

# Discussion

## Future directions

There may be some practical utility to pursue training interventions aimed at *how* characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.[^check] Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

[^check]: Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion

### 2022-12-02 Submission.tex
formatting mostly

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, Renata Garcia Prieto Palacios Roji2, \& John Kulas2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. In fact, A. B. Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory. The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al. (2000)). Cavanaugh et al. (2000) delineated between two forms of demands -- that of \emph{challenge} and \emph{hindrance} demands. Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., Cavanaugh et al. (2000)).

However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals. In fact, this is one of several issues raised by @ mazzola2019should in a recent review and meta-analysis of this framework. These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both -- challenge and hindrance appraisals. LePine (2022), in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.

@@

We used 98 statements taken from O*NET \href{https://www.O*NETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}. We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements). 57 ``work context'' statements grouped into ``Interpersonal Relationships'' (14 statements), ``Physical Work Conditions'' (30 statements), and ``Structural Job Characteristics'' (13 statements).

These ``descriptors'' often have unique response categories (\href{https://www.O*NETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}). We retained the O*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

The below graphs present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.

\begin{quote}
Note. The ``zero'' standard deviations are likely one person, \emph{n}'s should also go on these graphs if they're retained.
\end{quote}

\includegraphics{Submission_files/figure-latex/resourceslowsd-1.pdf}

\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}

\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}

@@

The below graphs present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

\includegraphics{Submission_files/figure-latex/resourceshisd-1.pdf}

\includegraphics{Submission_files/figure-latex/challengeshighsd-1.pdf}

\includegraphics{Submission_files/figure-latex/hindranceshighsd-1.pdf}

\begin{verbatim}
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
##   1.000   1.000   2.000   2.185   3.000   5.000       7
\end{verbatim}

\begin{verbatim}
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
##   1.000   4.000   4.500   4.202   5.000   5.000       7
\end{verbatim}

\begin{verbatim}
##    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
##   1.000   4.000   4.500   4.205   5.000   5.000       7
\end{verbatim}

\begin{verbatim}
## 
##             Autonomy    Emotional Demands          Job Control 
##                 1704                 1704                 1704 
##             Overwork        Participation Physical Environment 
##                 1704                 1704                 1704 
##    Recipient Contact        Team Cohesion        Time Pressure 
##                 1704                 1704                 1704 
##        Work Pressure 
##                 1704
\end{verbatim}

@@

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Job Demands-Resources model components through the lens of O*NET classifications},
  pdfauthor={Alicia Stachowski1, John Kulas2, \& Renata Garcia Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

Although there is a tendency to attach a negative connotation to the word ``stress'', Selye (1936) defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. In fact, A. B. Bakker and Demerouti (2017) call attention to different types of demands in their recent review of, and future directions, for work on the job-demands resources theory.

The challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people feel about a given stressor (Cavanaugh et al. (2000)). Cavanaugh et al. (2000) delineated between two forms of demands -- that of \emph{challenge} and \emph{hindrance} demands. Challenge demands promote mastery, personal growth, and future gains -- these stressors should lead to coping strategies that facilitate achievement. Stressors like time pressure and responsibility are considered challenge stressors/demands. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Hindrance stressors (e.g., role conflict, role ambiguity, politics) are associated with negative job behaviors and attitudes. This particular distinction between challenges and hindrances has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hindrance stressors, negative outcomes (e.g., Cavanaugh et al. (2000)).

However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals. In fact, this is one of several issues raised by Mazzola and Disselhorst (2019) in a recent review and meta-analysis of this framework. These authors cited the apriori assignment to stressors as a challenge or hindrance as a flawed assumption, suggesting that stressors are more likely to be a combination of both -- challenge and hindrance appraisals. LePine (2022), in a rebuttal to the @ mazzola2019should criticism, while acknowledging that the original challenge-hindrance stressor framework was based on the assertion that people tend to appraise specific work stressors ad challenges and other demands, noted that the appraisals likely served as a mediator.

@@

We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{``activity'' and ``context'' classifications}. We retained 41 ``work activity'' classifications which O*NET groups into categories of ``Information Input'' (5 statements), ``Interacting with Others'' (17 statements), ``Mental Processes'' (10 statements) and ``Work Output'' (9 statements). 57 ``work context'' statements grouped into ``Interpersonal Relationships'' (14 statements), ``Physical Work Conditions'' (30 statements), and ``Structural Job Characteristics'' (13 statements).

These ``descriptors'' often have unique response categories (\href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{see here for example}). We retained the O*NET wording to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/resourcesagree-1.pdf}
\caption{\label{fig:resourcesagree}Characteristics most similarly viewed as resources (lowest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/challengesagree-1.pdf}
\caption{\label{fig:challengesagree}Characteristics most similarly viewed as challenges (lowest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/hindrancesagree-1.pdf}
\caption{\label{fig:hindrancesagree}Characteristics most similarly viewed as hindrances (lowest standard deviations).}
\end{figure}

Figures \ref{fig:resourcesagree}, \ref{fig:challengesagree}, and \ref{fig:hindrancesagree} present the resources, challenges, and hindrances that are \emph{largely agreed on} as indexed by (relatively) low standard deviations.\footnote{There were a few characteristics with standard deviations of ``zero'' but these were excluded from presenation as they were likely representing only one person (\emph{n}'s should also go on these graphs if they're retained - Alicia's idea 12/2 was to use initial ratings as indicators of counts).}

@@

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/resourcesdisagree-1.pdf}
\caption{\label{fig:resourcesdisagree}Characteristics most \emph{dis}similarly viewed as resources (highest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/challengesdisagree-1.pdf}
\caption{\label{fig:challengesdisagree}Characteristics most \emph{dis}similarly viewed as challenges (highest standard deviations).}
\end{figure}

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/hindrancesdisagree-1.pdf}
\caption{\label{fig:hindrancesdisagree}Characteristics most \emph{dis}similarly viewed as hindrances (highest standard deviations).}
\end{figure}

Figures \ref{fig:resourcesdisagree}, \ref{fig:challengesdisagree}, and \ref{fig:hindrancesdisagree} present the resources, challenges, and hindrances that are \emph{largely disagreed on} as indexed by (relatively) high standard deviations (these are the 10 characteristics with the greatest variability in rating).

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{future-directions}{%
\subsection{Future directions}\label{future-directions}}

There may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.\footnote{Check on this - this is just speculative place-holding from 12/2 Hudson coffee discussion} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

@@

\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.
